---
title: "Gapminder plots"
author: "Sarafa Iyaniwura"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    keep_md: yes
---

Let us beging by loading the necessary packages required for this exercise

```{r}
suppressPackageStartupMessages(library(tidyverse))
library(ggplot2)
```


We begin by loading the extracted gapminder data for Nigeria only from the `gap_extract.csv` file. Let us use this data for some exercise

```{r}
gap_data <- read.csv(file="gap_extract.csv", header = TRUE, sep=",")
```

Let us display the structure of the data frame we extracted:

```{r}
str(gap_data)
```

we can also view the first few rows of the data 

```{r}
gap_data %>% 
	head() %>%
	knitr::kable()
```

Let us plot the `gdpPercap` vs `LifeExp`

```{r}
gap_data %>%
	ggplot(aes(lifeExp,gdpPercap) ) + 
	geom_point() +  ggtitle("Gdp per Cap vs Life expectancy for Nigeira")
```

Let us plot the `pop` vs `LifeExp`

```{r}
gap_data %>%
	ggplot(aes(lifeExp,pop) ) + 
	geom_point() +  ggtitle("Population vs Life expectancy for Nigeira")
```


Let us extract some columns of the `gad_data` and write it into a file in `.csv` format

```{r}
Nig_data <- gap_data %>%
	select(year,gdpPercap,pop,lifeExp)

write.csv(Nig_data,"Nig_data.csv",row.names = FALSE, quote = FALSE)

```


