---
title: "Gapminder time series"
author: "Sarafa Iyaniwura"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    keep_md: yes
---

Let us beging by loading the necessary packages required for this exercise

```{r}
suppressPackageStartupMessages(library(tidyverse))
library(ggplot2)
```


We begin by loading the extracted  data frame from the `Nig_data.csv` file. We shall use the data to produce time series graphs of `gdpPercap`, `lifeExp`, and `pop` (population)

```{r}
Nig_df <- read.csv(file="Nig_data.csv", header = TRUE, sep=",")
```


we can also view the first few rows of the data as follows

```{r}
Nig_df %>% 
	head() %>%
	knitr::kable()
```

Let us plot the `gdpPercap` for Nigeria over time from 1952 to 2007

```{r}
Nig_df %>%
	ggplot(aes(year,gdpPercap) ) +  
	geom_point() +  ggtitle("Time series of gdp per capital for Nigeria")
```

`lifeExp` for Nigeria over time from 1952 to 2007

```{r}
Nig_df %>%
	ggplot(aes(year,lifeExp ))  + 
	geom_point() +  ggtitle("Time series of  life expectancy of Nigeira")
```


`pop` for Nigeria over time from 1952 to 2007

```{r}
Nig_df %>%
	ggplot(aes(year,pop)) + 
	geom_point() +  ggtitle("Time series of population of Nigeira")

```


